### 2021-11-25 appendix3/appendix.tex
begin rearranging appendix 3

%!TEX root = ../thesis.tex
\chapter{Convergence without ephemeral phases\label{app:extend conv}}
For completeness, we include here, the results needed to prove the convergence of the QBD-RAP scheme without the need for the ephemeral initial states.

@@

\begin{thm}\label{thm: a thm2!}
	As \(p\to \infty\) the following convergence statements hold.
	For \(r\in\{+,-\},\, q\in\{+0,-0\}\) and \(m=0\),  
	\begin{align}\int_{x\in\calD_{\ell_0}}\widehat f_{0,q,r}^{\ell_0,(p)}(\lambda)(x,j;x_0,k)\psi(x)\wrt x \to \int_{x\in\calD_{\ell_0}}\widehat \mu_{0,q,r}^{\ell_0}(\lambda)(x,j;x_0,k)\psi(x)\wrt x.\end{align}
	For \(r\in\{+,-\},\, q\in\{+0,-0\}\) and \(m\geq 1\), 
	\begin{align}\int_{x\in\calD_{\ell_0}}\widehat f_{m,q,r}^{\ell_0,(p)}(\lambda)(x,j;x_0,k)\psi(x)\wrt x \to \int_{x\in\calD_{\ell_0}}\widehat \mu_{m,q,r}^{\ell_0}(\lambda)(x,j;x_0,k)\psi(x)\wrt x.\label{eqn: thm 22}\end{align}
\end{thm}
\begin{proof}
	\textit{Cases \((q,r) \in \{(+0,-),(-0,+)\}\), and \(m=0\).} First, take \(q=-0\) and \(r=+\), then 
	\begin{align}
		&\int_{x\in\calD_k}\widehat{f}_{0,-0,+}^{\ell_0,(p)}(\lambda)(x,j;x_0,k)\psi(x)\wrt x \nonumber 
		\\&:=\int_{x_1=0}^\infty \int_{x\in\calD_k} \bs e_k [\bs I - \bs T_{00}]^{-1}\bs T_{0+} \bs M^0_{++}(\lambda,x_1)\bs e_j \nonumber
		\bs a_{\ell_0,k}^{(p)}(x_0) \bs D^{(p)} \bs N^{1,(p)}(\lambda,x_1) 
		\\& {\bs v}^{(p)}(y_{\ell_0+1}-x)\psi(x)\wrt x\wrt x_{1}  \nonumber
		\\& + \int_{x_1=0}^\infty\int_{x_2=0}^\infty \int_{x\in\calD_k}  \bs e_k [\bs I - \bs T_{00}]^{-1}\bs T_{0-} \bs M^1_{-+}(\lambda,x_1,x_{2})\bs e_j \nonumber
		\bs a_{\ell_0,k}^{(p)}(x_0)\bs N^{2,(p)}(\lambda,x_1,x_{2}) 
		\\& {\bs v}^{(p)}(y_{\ell_0+1}-x)\psi(x)\wrt x\wrt x_{2} \wrt x_1. \label{eqn: thm 1223}
	\end{align}
	The second term is a linear combination of \(\int_{x\in\calD_k}\widehat{f}_{1,-,+}^{\ell_0,(p)}(\lambda)(x,j;x_0,i) \psi(x)\wrt x\) terms, each of which converge to \(\int_{x\in\calD_k}\widehat{\mu}_{1,-,+}^{\ell_0,(p)}(\lambda)(x,j;x_0,i) \psi(x)\wrt x\), by the case we proved in Theorem~\ref{thm: a thm!}. As for the first term, it is a linear combination of terms
	\[\int_{x_1=0}^\infty \int_{x\in\calD_k} \bs e_i \bs H^{++}(\lambda,x_1)\bs e_j \nonumber
	\bs a_{\ell_0,k}^{(p)}(x_0) \bs D^{(p)} e^{\bs S^{(p)}x_1} 
	{\bs v}^{(p)}(y_{\ell_0+1}-x)\psi(x)\wrt x\wrt x_{1}.\]
	Lemma~\ref{lem: ppp} proves that such terms converge to \(\int_{x\in\calD_k}\widehat{\mu}_{0,+,+}^{\ell_0}(\lambda)(x,j;x_0,i) \psi(x)\wrt x\). Therefore (\ref{eqn: thm 1223}) is a finite linear combination of terms, each of which converge, hence (\ref{eqn: thm 1223}) converges and converges to 
	\begin{align}
		&\int_{x_1=0}^\infty \int_{x\in\calD_k} \bs e_k \sum_{i\in\calS_+} [\bs I - \bs T_{00}]^{-1}\bs T_{0i}\int_{x\in\calD_k}\widehat{\mu}_{0,+,+}^{\ell_0}(\lambda)(x,j;x_0,i) \psi(x)\wrt x \nonumber
		\\& + \int_{x_1=0}^\infty\int_{x_2=0}^\infty \int_{x\in\calD_k} \sum_{i\in\calS_-}\bs e_k [\bs I - \bs T_{00}]^{-1}\bs T_{0i}\int_{x\in\calD_k}\widehat{\mu}_{1,-,+}^{\ell_0}(\lambda)(x,j;x_0,i) \psi(x)\wrt x, \label{eqn: thm 1223B}
	\end{align}
	which is \(\widehat{\mu}_{0,-0,+}^{\ell_0}(\lambda)(x,j;x_0,k)\). This proves the result for \(r=+\) and \(q=-0\). Analogous arguments prove the result for \(r=-\) and \(q=+0\).

@@

\section{Technical results}

\begin{lem}\label{lem: ppp}
	Let \(\psi:\calD_{\ell_0}\to \mathbb R\) be bounded \(|\psi(x)|\leq F\) and Lipschitz continuous function and let \(\lambda >0\). For \(i\in\mathcal S_-,j\in\mathcal S_-\cup\calS_{-0}\), \(x_0\in(0,\Delta)\), 
	\begin{align}
		&\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\bs k^{(p)}(x_0) \bs D^{(p)} e^{\bs S x_1} {\bs v}^{(p)}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x \wrt x_1  
		\to \int_{x=0}^{x_0} h_{ij}^{--}(\lambda,x_0-x)\psi(x)\wrt x, \label{eqn: LLLlllL}
	\end{align}
	as \(p\to\infty\). Similarly, for \(i\in\mathcal S_+,j\in\mathcal S_+\cup\calS_{+0}\)
	\begin{align}
		&\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\bs k^{(p)}(x_0) \bs D^{(p)} e^{\bs S^{(p)} x_1} {\bs v}^{(p)}(x) h_{ij}^{++}(\lambda, x_1) \psi(\Delta-x) \wrt x \wrt x_1  \nonumber 
		\\&\to\int_{x=\Delta-x_0}^{\Delta} h_{ij}^{++}(\lambda,x-x_0)\psi(x)\wrt x, \label{eqn: LLLlllL2222}
	\end{align}
\end{lem}
\begin{proof}
	Assume, without loss of generality \(\ell_0=0\) so \(\calD_{\ell_0}=[0,\Delta]\). Substituting the definition of \(\bs D\), then the left-hand side of (\ref{eqn: LLLlllL}) is
	\begin{align}
%		&\Bigg|\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\bs k^{(p)}(x_0) \bs D^{(p)} e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x \wrt x_1\nonumber
%		 - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| \nonumber
		%
		&\Bigg|\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\int_{u=0}^\infty \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x \wrt x_1\nonumber
		\\&{}\qquad {} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x\Bigg| \nonumber
		%
		\\&\leq \Bigg|\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x \wrt x_1\nonumber
		\\&{}\qquad {} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x\Bigg| \nonumber
		%
		\\&\qquad {}+\Bigg|\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x \wrt x_1\Bigg| \label{eqn: llllL}
	\end{align}
	Since \(|\psi(x)|\leq F\) and \(|h_{ij}^{--}(\lambda,x)|\leq G\), the third term in (\ref{eqn: llllL}) is less than or equal to 
	\begin{align}
		&\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u e^{\bs S x_1} {\bs v}(x) \wrt x \wrt x_1G F.\label{eqn: a big lola}
	\end{align} 
	Computing the integral over \(x_1\) in (\ref{eqn: a big lola}) gives
	\begin{align}
		& \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \bs k(u) \wrt u (-\bs S)^{-1}{\bs v}(x) \wrt x G F\nonumber
		%
		\\&\leq  \int_{x=0}^{\Delta}\int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s \wrt u \wrt x G_{\bs v} G F \nonumber
		%
		\\&= \int_{u= \Delta-\varepsilon}^\infty  \bs k(x_0)e^{\bs Su}\bs s  \wrt u\Delta G_{\bs v} G F.\label{eqn: google the yes}
	\end{align}
	since, by property \ref{properties: 1}, \(\bs k(u)(-\bs S)^{-1}{\bs v}(x)\leq \bs k(u)\bs e G_{\bs v}=G_{\bs v}\). The bound (\ref{eqn: google the yes}) is equal to 
	\begin{align}
		\Delta \mathbb P(Z>x_0 + \Delta-\varepsilon) \wrt x G_{\bs v} G F
		\leq  \Delta \cfrac{\var(Z)}{(x_0-\varepsilon)^2} G_{\bs v} G F, \label{eqn: JjJ}
	\end{align}
	by Chebyshev's inequality.

@@

		&\Bigg|\int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \wrt x_1 \wrt u \psi(x) \wrt x \nonumber
		\\&{}\qquad {} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x\Bigg| \nonumber
		\\&=\Bigg|\int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \left[ h_{ij}^{--}(\lambda, \Delta - u - x)1(u+x\leq \Delta-\varepsilon) + r_{\bs v}(u,x) \right] \psi(x) \wrt u \wrt x \nonumber

@@

		\\&\qquad{} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| + \Bigg| \int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s r_{\bs v}(u,x) \psi(x) \wrt u \wrt x \Bigg|

@@

	where the first equality holds from Property \ref{properties: 2}. The last term in (\ref{eqn: aKK}) is less than or equal to 

@@

		\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su} \int_{x=0}^{\Delta} \bs s \left|r_{\bs v}(u,x)\right|\wrt x \wrt u F 
		&\leq \int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su} \bs sR_{{\bs v},2} \wrt u F \nonumber 
		\\&\leq R_{{\bs v},2} F, \label{eqn: HhHj}

@@

	by Property \ref{properties: 2}. The first two terms in (\ref{eqn: aKK}) are 
		& \Bigg|\int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x)1(u+x\leq \Delta-\varepsilon) \psi(x) \wrt u \wrt x \nonumber
		\\&\qquad{} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| \nonumber 
		\\&= \Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=0}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \wrt x \nonumber
		  \\&\qquad{}- \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| \nonumber 
		\\&\leq \Bigg| \int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x_0+\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u 1(\Delta-x_0+\varepsilon\leq \Delta-x-\varepsilon) \wrt x\nonumber
		\\&\qquad{} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| \nonumber 
		\\&\qquad {}+\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=0}^{\min(\Delta-x_0-\varepsilon,\Delta-x-\varepsilon)} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \wrt x\Bigg|\nonumber
		\\&\qquad {}+\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0+\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \nonumber 
		\\&\qquad\qquad \times1(\Delta-x_0+\varepsilon\leq \Delta - x -\varepsilon)\wrt x\Bigg|\nonumber
		\\&\qquad {}+\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \nonumber
		\\&\qquad\qquad \times 1(\Delta-x_0-\varepsilon\leq \Delta - x -\varepsilon < \Delta-x_0+\varepsilon)\wrt x\Bigg|   \label{eqn: LLkkK}

>>>>

%!TEX root = ../thesis.tex
\chapter{Convergence without ephemeral phases\label{app:extend conv}}
For completeness, we include here proof of the convergence of the QBD-RAP scheme to the fluid queue without the need for the ephemeral initial states.

@@

Theorem~\ref{thm: a thm2!} below is analogous to Theorem~\ref{thm: a thm!} and proves a certain convergence of the QBD-RAP scheme to the fluid queue in the case that \(\phi(0)\in\mathcal S_{+0}\cup\calS_{-0}\). Like the proof of Theorem~\ref{thm: a thm!}, the proof of Theorem~\ref{thm: a thm2!} relies on technical bounds which we establish with the remainder of this Appendix.

\begin{thm}\label{thm: a thm2!}
	As \(p\to \infty\), for \(q\in\{+0,-0\},\, r\in\{+,-\}\) and \(m=0\),  
	\begin{align}\int_{x\in\calD_{\ell_0}}\widehat f_{0,q,r}^{\ell_0,(p)}(\lambda)(x,j;x_0,k)\psi(x)\wrt x \to \int_{x\in\calD_{\ell_0}}\widehat \mu_{0,q,r}^{\ell_0}(\lambda)(x,j;x_0,k)\psi(x)\wrt x.\end{align}
	For \(q\in\{+0,-0\}, r\in\{+,-\}\) and \(m\geq 1\), 
	\begin{align}\int_{x\in\calD_{\ell_0}}\widehat f_{m,q,r}^{\ell_0,(p)}(\lambda)(x,j;x_0,k)\psi(x)\wrt x \to \int_{x\in\calD_{\ell_0}}\widehat \mu_{m,q,r}^{\ell_0}(\lambda)(x,j;x_0,k)\psi(x)\wrt x.\label{eqn: thm 22}\end{align}
\end{thm}
\begin{proof}
	\textit{Cases \((q,r) \in \{(+0,-),(-0,+)\}\), and \(m=0\).} First, take \(q=-0\) and \(r=+\), then 
	\begin{align}
		&\int_{x\in\calD_k}\widehat{f}_{0,-0,+}^{\ell_0,(p)}(\lambda)(x,j;x_0,k)\psi(x)\wrt x \nonumber 
		\\&:=\int_{x_1=0}^\infty \int_{x\in\calD_k} \bs e_k [\bs I - \bs T_{00}]^{-1}\bs T_{0+} \bs M^0_{++}(\lambda,x_1)\bs e_j \nonumber
		\bs a_{\ell_0,k}^{(p)}(x_0) \bs D^{(p)} \bs N^{1,(p)}(\lambda,x_1) 
		\\& {\bs v}^{(p)}(y_{\ell_0+1}-x)\psi(x)\wrt x\wrt x_{1}  \nonumber
		\\& + \int_{x_1=0}^\infty\int_{x_2=0}^\infty \int_{x\in\calD_k}  \bs e_k [\bs I - \bs T_{00}]^{-1}\bs T_{0-} \bs M^1_{-+}(\lambda,x_1,x_{2})\bs e_j \nonumber
		\bs a_{\ell_0,k}^{(p)}(x_0)\bs N^{2,(p)}(\lambda,x_1,x_{2}) 
		\\& {\bs v}^{(p)}(y_{\ell_0+1}-x)\psi(x)\wrt x\wrt x_{2} \wrt x_1. \label{eqn: thm 1223}
	\end{align}
	The second term is a linear combination of \(\int_{x\in\calD_k}\widehat{f}_{1,-,+}^{\ell_0,(p)}(\lambda)(x,j;x_0,i) \psi(x)\wrt x\) terms, each of which converge to \(\int_{x\in\calD_k}\widehat{\mu}_{1,-,+}^{\ell_0,(p)}(\lambda)(x,j;x_0,i) \psi(x)\wrt x\), by the case we proved in Theorem~\ref{thm: a thm!}. As for the first term, it is a linear combination of terms
	\[\int_{x_1=0}^\infty \int_{x\in\calD_k} \bs e_i \bs H^{++}(\lambda,x_1)\bs e_j \nonumber
	\bs a_{\ell_0,k}^{(p)}(x_0) \bs D^{(p)} e^{\bs S^{(p)}x_1} 
	{\bs v}^{(p)}(y_{\ell_0+1}-x)\psi(x)\wrt x\wrt x_{1}.\]
	Lemma~\ref{lem: ppp} proves that such terms converge to \(\int_{x\in\calD_k}\widehat{\mu}_{0,+,+}^{\ell_0}(\lambda)(x,j;x_0,i) \psi(x)\wrt x\). Therefore (\ref{eqn: thm 1223}) is a finite linear combination of terms, each of which converge, hence (\ref{eqn: thm 1223}) converges and converges to 
	\begin{align}
		&\int_{x_1=0}^\infty \int_{x\in\calD_k} \bs e_k \sum_{i\in\calS_+} [\bs I - \bs T_{00}]^{-1}\bs T_{0i}\int_{x\in\calD_k}\widehat{\mu}_{0,+,+}^{\ell_0}(\lambda)(x,j;x_0,i) \psi(x)\wrt x \nonumber
		\\& + \int_{x_1=0}^\infty\int_{x_2=0}^\infty \int_{x\in\calD_k} \sum_{i\in\calS_-}\bs e_k [\bs I - \bs T_{00}]^{-1}\bs T_{0i}\int_{x\in\calD_k}\widehat{\mu}_{1,-,+}^{\ell_0}(\lambda)(x,j;x_0,i) \psi(x)\wrt x, \label{eqn: thm 1223B}
	\end{align}
	which is \(\widehat{\mu}_{0,-0,+}^{\ell_0}(\lambda)(x,j;x_0,k)\). This proves the result for \(r=+\) and \(q=-0\). Analogous arguments prove the result for \(r=-\) and \(q=+0\).

@@

\section{Technical results}
As in Appendix~\ref{app:tand}, we treat the cases of \(m=0\) and \(m\geq 1\) seperately. We start with the case \(m=0\). The following result is analgous to Lemma~\ref{lem: Dcoajc}, though the proof is somewhat more tedious.

\begin{lem}\label{lem: ppp}
	Let \(\psi:\calD_{\ell_0}\to \mathbb R\) be bounded \(|\psi(x)|\leq F\) and Lipschitz continuous function and let \(\lambda >0\). For \(i\in\mathcal S_-,j\in\mathcal S_-\cup\calS_{-0}\), \(x_0\in(0,\Delta)\), 

@@

		&\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\bs k^{(p)}(x_0) \bs D^{(p)} e^{\bs S x_1} {\bs v}^{(p)}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x \wrt x_1  
		\to \int_{x=0}^{x_0} h_{ij}^{--}(\lambda,x_0-x)\psi(x)\wrt x, \label{eqn: LLLlllL}
	as \(p\to\infty\). Similarly, for \(i\in\mathcal S_+,j\in\mathcal S_+\cup\calS_{+0}\)
		&\int_{x_1=0}^\infty \int_{x=0}^{\Delta}\bs k^{(p)}(x_0) \bs D^{(p)} e^{\bs S^{(p)} x_1} {\bs v}^{(p)}(x) h_{ij}^{++}(\lambda, x_1) \psi(\Delta-x) \wrt x \wrt x_1  \nonumber 
		\\&\to\int_{x=\Delta-x_0}^{\Delta} h_{ij}^{++}(\lambda,x-x_0)\psi(x)\wrt x, \label{eqn: LLLlllL2222}
\end{lem}
\begin{proof}
	Assume, for simplicity and without loss of generality, that \(\ell_0=0\) so \(\calD_{\ell_0}=[0,\Delta]\). Substituting the definition of \(\bs D\) and exchanging the order of integration, then the left-hand side of (\ref{eqn: LLLlllL}) is
		&\Bigg|\int_{u=0}^\infty \bs k(x_0)e^{\bs Su}\bs s \int_{x=0}^{\Delta}  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x_1 \wrt x \wrt u\nonumber
		\\&{}\qquad {} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x\Bigg|.\label{eqn: aksfKJJJJJ}
	We wish to apply Property~\ref{properties: 2} to the integral over \(x_1\), however, to do so requires that \(u\leq \Delta-\varepsilon\). Breaking up the integral with respect to \(u\), then (\ref{eqn: aksfKJJJJJ}) is equal to 
		&\Bigg|\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \int_{x=0}^{\Delta}  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x_1 \wrt x \wrt u + d_1 \nonumber
		\\&{}  - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x\Bigg|
		\\&\leq \Bigg|\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \int_{x=0}^{\Delta}  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x_1 \wrt x \wrt u\nonumber
		\\&{} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x\Bigg| +|d_1| \label{eqnL MMMM}
	where 
	\[|d_1|=\left|\int_{u=\Delta-\varepsilon}^\infty \bs k(x_0)e^{\bs Su}\bs s \int_{x=0}^{\Delta}  \int_{x_1=0}^\infty \bs k(u)  e^{\bs S x_1} {\bs v}(x) h_{ij}^{--}(\lambda, x_1) \psi(x) \wrt x_1 \wrt x \wrt u\right|.\]
	We show later that \(|d_1|\) can be made arbitrarily small by choosing \(Z\) with sufficiently small variance.  For now, let us focus on the first absolute value in (\ref{eqnL MMMM}). By Property~\ref{properties: 2} the first absolute value in (\ref{eqnL MMMM}) is 
		&\Bigg|\int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s \left[ h_{ij}^{--}(\lambda, \Delta - u - x)1(u+x\leq \Delta-\varepsilon) + r_{\bs v}(u,x) \right] \psi(x) \wrt u \wrt x \nonumber

@@

		\\&\qquad{} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| + |d_2|,

@@

	where 
	\[|d_2| = \left| \int_{x=0}^{\Delta}\int_{u=0}^{\Delta-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s r_{\bs v}(u,x) \psi(x) \wrt u \wrt x \right|.\]
	We show later that \(|d_2|\) can be made arbitrarily small by choosing \(Z\) with sufficiently small variance. The remaining term in (\ref{eqn: aKK}) can be written as 

@@

		&\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=0}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \wrt x 
		- \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg|.\label{eqn: FGHJKL}

@@

	Intuitively, when the variance of \(Z\) is low, we expect a significant constribution to the integral with respect to \(u\) in (\ref{eqn: FGHJKL}) to come from the portion of the integral over the interval \((\Delta-x_0-\varepsilon,\Delta-x_0+\varepsilon)\). Although, the integral with respect to \(u\) only contain this interval when \(x\) is sufficiently small. Breaking up the integral with respect to \(u\) in (\ref{eqn: FGHJKL}) into an integral over the interval \((\Delta-x_0-\varepsilon,\Delta-x_0+\varepsilon)\) and integrals over the rest, then applying the triangle inequality, (\ref{eqn: FGHJKL}) is less than or equal to 
	\begin{align}
		&\Bigg| \int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x_0+\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u 1(x\leq x_0-2\varepsilon) \wrt x\nonumber
		\\&\qquad{} - \int_{x=0}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| + |d_3|+|d_4|+|d_5|,\label{eqn: LLkkK} 
	\intertext{where}
		&|d_3|=\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=0}^{\min(\Delta-x_0-\varepsilon,\Delta-x-\varepsilon)} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \wrt x\Bigg|,\nonumber
		\\&|d_4|=\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0+\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \nonumber 
		 1(x\leq x_0-2\varepsilon)\wrt x\Bigg|,\nonumber
		\\&|d_5|=\Bigg|\int_{x=0}^{\Delta-\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x-\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u \times 1(x\in[x_0,x_0-2\varepsilon))\wrt x\Bigg|.  \nonumber 
	\end{align}
	We show later that \(|d_3|,\, |d_4|\) and \(|d_5|\) can be made arbitrarily small by choosing \(Z\) with sufficiently small variance.

	In the first integral with respect to \(x\) in (\ref{eqn: LLkkK}), since \(x_0\in(2\varepsilon,\Delta-\varepsilon)\), then we can absorb the indicator function into the limits of the integral which results in
	\begin{align}
		\int_{x=0}^{x_0-2\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x_0+\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u 1(x\leq x_0-2\varepsilon) \wrt x.
	\end{align}
	With this, and breaking up the integral over \(h_{ij}^{--}\), we can write the first absolute value in (\ref{eqn: LLkkK}) as 
	\begin{align}
		\nonumber &\Bigg| \int_{x=0}^{x_0-2\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x_0+\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u  \wrt x 
		\\\nonumber &\qquad{} - \int_{x=0}^{x_0-2\varepsilon} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x  - \int_{x=x_0-2\varepsilon}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| 
		\\\nonumber &\leq \Bigg| \int_{x=0}^{x_0-2\varepsilon}\int_{u=\Delta-x_0-\varepsilon}^{\Delta-x_0+\varepsilon} \bs k(x_0)e^{\bs Su}\bs s h_{ij}^{--}(\lambda, \Delta - u - x) \psi(x) \wrt u   \wrt x 
		\\&\qquad{} - \int_{x=0}^{x_0-2\varepsilon} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \Bigg| + |d_6|,\label{eqn:PPPPPP}
	\end{align}
		where
	\begin{align}
		&|d_6|=\left|\int_{x=x_0-2\varepsilon}^{x_0} h_{ij}^{--}(\lambda, x_0 - x)\psi(x)\wrt x \right|.\nonumber 
	\end{align}
	We show later that \(|d_6|\) can be made arbitrarily small by choosing \(Z\) with sufficiently small variance.
